A generalized definition of multidimensional item response theory parameters

### 2022-05-20 output/paper_draft/paper_M2PLM_parameters.Rmd
lavaan package is not being used so it's not written to the bibliography

```{r write-bib, cache=TRUE}
# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown', 'lavaan'),
  'www/packages.bib'
)
```

>>>>

```{r write-bib, cache=TRUE}
# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'www/packages.bib'
)
```
